Comparative effectiveness of BNT162b2 versus Moderna booster doses in England: preliminary report

### 2022-04-23 write-up/report.Rmd
use new fct_Recdoerelevel function

@@

km_estimates <- read_csv(here("output", "release-objects", matchset, "km_estimates.csv")) %>% 
  mutate(
    outcome_descr = fct_recode(as.character(outcome),  !!!recoder$outcome),
    subgroup_descr = fct_recode(subgroup,  !!!recoder$subgroup),
    subgroup_level_descr = replace_na(subgroup_level_descr, "")
  )
km_contrasts_daily <- read_csv(here("output", "release-objects", matchset, "km_contrasts_daily.csv")) %>% 
  mutate(
    outcome_descr = fct_recode(as.character(outcome),  !!!recoder$outcome),
    subgroup_descr = fct_recode(subgroup,  !!!recoder$subgroup),
    subgroup_level_descr = replace_na(subgroup_level_descr, "")
  )
km_contrasts_overall <- read_csv(here("output", "release-objects", matchset, "km_contrasts_overall.csv")) %>% 
  mutate(
    outcome_descr = fct_recode(as.character(outcome),  !!!recoder$outcome),
    subgroup_descr = fct_recode(subgroup,  !!!recoder$subgroup),
    subgroup_level_descr = replace_na(subgroup_level_descr, "")
  )

@@

`r label_number(1, big.mark=",")(filter(match_flowchart, crit=="c0") %>% pull(n) %>% sum)` adults registered at a TPP practice received a booster vaccination of either BNT162b2 (`r label_number(1, big.mark=",")(filter(match_flowchart, crit=="c0", vax3_type=="pfizer") %>% pull(n))`) or Moderna (`r label_number(1, big.mark=",")(filter(match_flowchart, crit=="c0", vax3_type=="moderna") %>% pull(n))`) during the study period, with `r label_number(1, big.mark=",")(filter(match_flowchart, crit=="c6", vax3_type="pfizer") %>% pull(n))` (`r label_percent(0.1)(filter(match_flowchart, crit=="c6", vax3_type="pfizer") %>% pull(pct_all))`) and `r label_number(1, big.mark=",")(filter(match_flowchart, crit=="c6", vax3_type="pfizer") %>% pull(n))` (`r label_percent(0.1)(filter(match_flowchart, crit=="c6", vax3_type="moderna") %>% pull(pct_all))`) eligible for matching. `r label_number(1, big.mark=",")(filter(match_flowchart, crit=="c7", vax3_type="pfizer") %>% pull(n))` were successfully matched in each group, `r label_percent(0.1)(filter(match_flowchart, crit=="c7", vax3_type="pfizer") %>% pull(pct_step))` and `r label_percent(0.1)(filter(match_flowchart, crit=="c7", vax3_type="moderna") %>% pull(pct_step))` respectively (Table 1, Figure 1).

@@

plot_coverage_cumuln <-
  match_coverage %>%
  mutate(
    treatment_descr = fct_recode(as.character(treatment), !!!recoder$treatment),
    status_descr = fct_recode(as.character(status), !!!recoder$status),
    cumuln = cumuln*((treatment*2) - 1)
  ) %>%
  ggplot()+
  geom_col(
    aes(
      x=vax3_date+0.5,
      y=cumuln,
      group=paste0(treatment,status_descr),
      fill=treatment_descr,
      alpha=status_descr,
      colour=NULL
    ),
    position=position_stack(reverse=TRUE),
    width=1
  )+
  geom_rect(xmin=xmin, xmax= xmax+1, ymin=-6, ymax=6, fill="grey", colour="transparent")+
  scale_x_date(
    breaks = unique(lubridate::ceiling_date(match_coverage$vax3_date, "1 month")),
    limits = c(xmin-1, NA),
    labels = scales::label_date("%d/%m"),
    expand = expansion(add=1),
  )+
  scale_y_continuous(
    labels = ~scales::label_number(accuracy = 1, big.mark=",")(abs(.)),
    expand = expansion(c(0, NA))
  )+
  scale_fill_brewer(type="qual", palette="Set2")+
  scale_colour_brewer(type="qual", palette="Set2")+
  scale_alpha_discrete(range= c(0.8,0.4))+
  labs(
    x="Date",
    y="Cumulative booster vaccines",
    colour=NULL,
    fill=NULL,
    alpha=NULL
  ) +
  theme_minimal()+
  theme(
    axis.line.x.bottom = element_line(),
    axis.text.x.top=element_text(hjust=0),
    strip.text.y.right = element_text(angle = 0),
    axis.ticks.x=element_line(),
    legend.position = "bottom"
  )+
  NULL

>>>>

## Import custom user functions from lib
source(here("lib", "functions", "utility.R"))

@@

km_estimates <- read_csv(here("output", "release-objects", matchset, "km_estimates.csv")) %>% 
  mutate(
    outcome_descr = fct_recoderelevel(as.character(outcome),  recoder$outcome),
    subgroup_descr = fct_recoderelevel(subgroup,  recoder$subgroup),
    subgroup_level_descr = replace_na(subgroup_level_descr, "")
  )
km_contrasts_daily <- read_csv(here("output", "release-objects", matchset, "km_contrasts_daily.csv")) %>% 
  mutate(
    outcome_descr = fct_recoderelevel(as.character(outcome),  recoder$outcome),
    subgroup_descr = fct_recoderelevel(subgroup,  recoder$subgroup),
    subgroup_level_descr = replace_na(subgroup_level_descr, "")
  )
km_contrasts_overall <- read_csv(here("output", "release-objects", matchset, "km_contrasts_overall.csv")) %>% 
  mutate(
    outcome_descr = fct_recoderelevel(as.character(outcome),  recoder$outcome),
    subgroup_descr = fct_recoderelevel(subgroup,  recoder$subgroup),
    subgroup_level_descr = replace_na(subgroup_level_descr, "")
  )

@@

`r label_number(1, big.mark=",")(filter(match_flowchart, crit=="c0") %>% pull(n) %>% sum)` adults registered at a TPP practice received a booster vaccination of either BNT162b2 (`r label_number(1, big.mark=",")(filter(match_flowchart, crit=="c0", vax3_type=="pfizer") %>% pull(n))`) or Moderna (`r label_number(1, big.mark=",")(filter(match_flowchart, crit=="c0", vax3_type=="moderna") %>% pull(n))`) during the study period, with `r label_number(1, big.mark=",")(filter(match_flowchart, crit=="c6", vax3_type=="pfizer") %>% pull(n))` (`r label_percent(0.1)(filter(match_flowchart, crit=="c6", vax3_type=="pfizer") %>% pull(pct_all))`) and `r label_number(1, big.mark=",")(filter(match_flowchart, crit=="c6", vax3_type=="pfizer") %>% pull(n))` (`r label_percent(0.1)(filter(match_flowchart, crit=="c6", vax3_type=="moderna") %>% pull(pct_all))`) eligible for matching. `r label_number(1, big.mark=",")(filter(match_flowchart, crit=="c7", vax3_type=="pfizer") %>% pull(n))` were successfully matched in each group, `r label_percent(0.1)(filter(match_flowchart, crit=="c7", vax3_type=="pfizer") %>% pull(pct_step))` and `r label_percent(0.1)(filter(match_flowchart, crit=="c7", vax3_type=="moderna") %>% pull(pct_step))` respectively (Table 1, Figure 1).

@@

plot_coverage_cumuln <-
  match_coverage %>%
  mutate(
    treatment_descr = fct_recoderelevel(as.character(treatment), recoder$treatment),
    status_descr = fct_recoderelevel(as.character(status), recoder$status),
    cumuln = cumuln*((treatment*2) - 1)
  ) %>%
  ggplot()+
  geom_col(
    aes(
      x=vax3_date+0.5,
      y=cumuln,
      group=paste0(treatment,status_descr),
      fill=treatment_descr,
      alpha=status_descr,
      colour=NULL
    ),
    position=position_stack(reverse=TRUE),
    width=1
  )+
  geom_rect(xmin=xmin, xmax= xmax+1, ymin=-6, ymax=6, fill="grey", colour="transparent")+
  scale_x_date(
    breaks = unique(lubridate::ceiling_date(match_coverage$vax3_date, "1 month")),
    limits = c(xmin-1, NA),
    labels = scales::label_date("%d/%m"),
    expand = expansion(add=1),
  )+
  scale_y_continuous(
    labels = ~scales::label_number(accuracy = 1, big.mark=",")(abs(.)),
    expand = expansion(c(0, NA))
  )+
  scale_fill_brewer(type="qual", palette="Set2")+
  scale_colour_brewer(type="qual", palette="Set2")+
  scale_alpha_discrete(range= c(0.8,0.4))+
  labs(
    x="Date",
    y="Cumulative booster vaccines",
    colour=NULL,
    fill=NULL,
    alpha=NULL
  ) +
  theme_minimal()+
  theme(
    axis.line.x.bottom = element_line(),
    axis.text.x.top=element_text(hjust=0),
    strip.text.y.right = element_text(angle = 0),
    axis.ticks.x=element_line(),
    legend.position = "bottom"
  )+
  NULL
